Construction and Reduction of the $L_\infty$ Algebra of Observables Associated with a BV-Module

### 2025-10-24 bv-triples-background.tex
Reduction Section almost done.
Slides complete.
Presentation done.

@@

  \begin{defblock}[Lie-Rinehart Algebra]
    A \underline{triple} $(A,\mathfrak{L},\rho)$ where
    \begin{itemize}[label=$\triangleright$]
      \item $A$ is a commutative, associative algebra,
      \item $\mathfrak{L}$ is an $A$-module and a Lie algebra,
      \item there is an anchor map $\rho: \mathfrak{L} \to \mathrm{Der}(A)$ satisfying the Leibniz rule:

@@

\end{frame}
\note[itemize]{
    \item Let ${A}$ be a commutative  algebra over a field $\mathbb{k}$.
  Denote by $\X(A)=\Der_{\mathbb{k}}(A)$ its Lie algebra of derivations, which naturally forms an $A$-submodule of $\End(A)$ with the action $A\action \End(A)$ given by postmultiplying with the element of $A$.
  \item In the context of differential geometry, a primary example is when $A = C^\infty(M)$, the algebra of smooth functions on a smooth manifold $M$. In this case, $\mathfrak{X}(A)$ is isomorphic to the standard $C^\infty(M)$-module of smooth vector fields on $M$, often denoted by $\mathfrak{X}(M)$.
  \item To generalize the above geometric structures, we introduce the algebraic counterparts of  "multivector fields " and  "differential forms with Cartan calculus. " 
  \item The anchor map $\rho: E \to \mathop{\mathrm{Der}}(A)$ abstractly encodes the notion of derivations of $A$ with an $A$-linear Lie bracket. 
  \item   In fact, Lie-Rinehart algebras are algebraic analogues of Lie algebroids (and every Lie algebroid gives a Lie-Rinehart algebra).
  \item singular foliations in the sense of Androulidakis and Skandalis can be viewed as Lie--Rinehart algebras
  \item a Lie--Rinehart algebra over $C^{\infty}(M)$ that is projective as a module is equivalent to a Lie algebroid,  
}
%-----------------------------------------------------------+

@@

  \begin{quote}
    \centering
    \emph{... generalize the structure of the exterior algebra of multivector fields ...}
  \end{quote}
  %
  \begin{defblock}[Gerstenhaber Algebra]
    A \underline{triple} $(G, \wedge, \lbrace\cdot,\cdot\rbrace)$ where
    \begin{itemize}[label=$\triangleright$]
		\item $G$ is a $\mathbb{Z}$-graded vector space;
		\item $\wedge : G \otimes G \to G$ is a graded commutative, associative product;
		\item $\{\blank,\blank\} :G[1]\otimes G[1]\to G[1]$ is a graded Lie bracket,
  \end{itemize}
Compatibility: The bracket is a derivation of $\wedge$:
	\begin{align*}\label{eq:Gerstenhaber-derivationProperty}
		\{a, b \wedge c\} = \{a, b\} \wedge c + (-1)^{(|a|-1)|b|} b \wedge \{a, c\}
		&& \forall~ a, b, c \in G.
	\end{align*}

@@

\end{frame}
\note[itemize]{
  \item  The bracket $\{\blank,\blank\}$ could also be reinterpreted as a degree $-1$ bracket on the desuspended $\Z$-graded vector space $G$, coincides with the definition of $1$-Poisson algebra of \cite{Cattaneo2006b}.
  \item The Schouten--Nijenhuis bracket is the unique graded Lie bracket satisfying the following properties:
\begin{itemize}
	\item It restricts to the given Lie bracket on $\Lambda_A^1 \mathfrak{L} = \mathfrak{L}$;
	\item It vanishes on $A = \Lambda_A^0 \mathfrak{L}$;
	\item It satisfies the graded Leibniz rule with respect to the wedge product.
\end{itemize}
%
Explicitly, for homogeneous elements $x_1, \dots, x_m, y_1, \dots, y_n \in \mathfrak{L}$ and $f \in A$, it is given by
\begin{align*}
	[x_1 \wedge \cdots \wedge x_m,\; y_1 \wedge \cdots \wedge y_n] 
	&= \sum_{i,j} (-1)^{i+j} [x_i, y_j] \wedge x_1 \wedge \cdots \widehat{x_i} \cdots \wedge x_m \wedge y_1 \wedge \cdots \widehat{y_j} \cdots \wedge y_n~.
\end{align*}
}
%-----------------------------------------------------------+

@@

  \begin{exblock}[Chevalley--Eilenberg Algebra]
    The Chevalley--Eilenberg algebra for the Lie-Rinehart algebra $(A,\mathfrak{L},\rho)$:
    $$
    \CE(\mathfrak{L}) := \left((\Lambda_A^\bullet \mathfrak{L})^*\right)^{\rev}$$

@@

%-----------------------------------------------------------+
\begin{frame}{BV-Modules}
  %
  \begin{quote}
    \centering
    \emph{... generalize the structure of (the de Rham) algebra ...}
  \end{quote}
  %
  \begin{defblock}[Batalin-Vilkovisky Module]
    Is a \underline{graded vector space} $V$ together with
    \begin{itemize}[label=$\triangleright$]
      \item a differential $\d: V^i \to V^{i+1}$ (i.e. $d^2=0$),
      \item a Gerstenhaber module structure over a Gerstenhaber algebra $(G, \wedge, \lbrace\cdot,\cdot\rbrace)$,
    \end{itemize}
    Compatibility wrt the Lie algebra action $\Lie:G\action V$: 
    $$
      \Lie_x = [\iota_x, \d]~, \qquad \forall x \in G~.
    $$
  \end{defblock}
  \vfill\pause

@@

%-----------------------------------------------------------+
\begin{frame}{Abstract Cartan Calculus}
  %
  \begin{quote}
    \centering
    \emph{BV-module $(V,\d)$ over $(G,\wedge,\lbrace\cdot,\cdot\rbrace)$ encode a full Cartan calculus}
  \end{quote}
  %
  \vfill\pause
  \begin{denotblock}
    \begin{itemize}
      \item $\d$ the degree $1$ differential on $V$;
	    \item $\iota$ the associative algebra action\footnote{$\iota_{x\wedge y}=\iota_x\iota_y~, \qquad \forall x,y\in G$.} of $(G,\wedge)$ on $V$;
  	  \item $\Lie$ the Lie algebra action\footnote{$\Lie_{x\wedge y}=\iota_x\Lie_y + (-1)^{|y|}\Lie_x \iota_y~, \qquad \forall  x,y\in G$.} of $(G,\{\blank,\blank\})$ on $V$ of degree $-1$.
    \end{itemize}   
  \end{denotblock}
  \vfill\pause

  \begin{lemblock}[Cartan identities]
 The operators $\d$, $\iota_x$, and $\Lie_x$ satisfy six graded commutation relations:
	%
  \begin{align*}
	  \d^2                            &= 0,            &&&
	\iota_X \iota_Y + \iota_Y \iota_X  &= 0 ~,         \\
\iota_X \d   +	\d \iota_X      &= \Lie_X ~,    &&&
	\d \Lie_X - \Lie_X \d          &= 0 ~,    \\
	\Lie_X \iota_Y - \iota_Y \Lie_X    &= \iota_{[X,Y]}~,  &&&
	\Lie_X \Lie_Y - \Lie_Y \Lie_X      &= \Lie_{[X,Y]}~. 
\end{align*}
	%
  \end{lemblock}
  \vfill\pause

  \begin{exblock}[Classical Cartan Calculus]
    \vspace{-0.5em}
    $$ A=C^\infty(M)~,  \quad \mathfrak{L}=\X(M)~,\quad
     G=\Lambda^\bullet \X(M)~, \quad V=\Omega^\bullet(M)~. $$
  \end{exblock}
  %
\end{frame}
\note[itemize]{
  \item 	A pair $(G, V)$ consisting of a Gerstenhaber algebra and a BV module is often called a \emph{Tsygan–Tamarkin–Nest noncommutative differential calculus}~\cite[Def.~4.4]{Tsygan2004}.
  \item Denote Gerstenhaber algebra structure on $G \oplus V^{\rev}$ by $(\star,\llbracket\blank,\blank\rrbracket)$. For a homogeneous element $x \in G$, denote by $\iota_x$ and $\Lie_x$ the corresponding operators on $V$.
  \item These actions are induced by restricting the Gerstenhaber structure $(\star,\llbracket\blank,\blank\rrbracket)$ on $G \oplus V^{\rev}$ to $G \otimes V^{\rev} \subset (G \oplus V^{\rev})^{\otimes 2}$.
 \item The associative action $\iota$ is defined by
	\[
	\morphism{\iota}{G \otimes V^{\rev}}{V^{\rev}}{(x,\alpha)}{\iota_x \alpha := x \star \alpha},
	\]
	and satisfies
	\[
	\iota_{x \wedge y} \alpha = \iota_x \iota_y \alpha \quad \text{and} \quad \iota_x \alpha = (-1)^{|x||\alpha|} \alpha \star x.
	\]

	\item The Lie action $\Lie$ is defined by
	\[
	\morphism{\Lie}{G \otimes V^{\rev}}{V^{\rev}[-1]}{(x,\alpha)}{\Lie_x \alpha := \llbracket x, \alpha \rrbracket},
	\]
	and satisfies
	\[
	\Lie_{\{x,y\}} \alpha = \Lie_x \Lie_y \alpha + (-1)^{(|x|-1)(|y|-1)} \Lie_y \Lie_x \alpha,
	\]
	as well as the graded antisymmetry identity
	\[
	\Lie_x \alpha = -(-1)^{|x||\alpha|} \llbracket \alpha, x \rrbracket.
	\]
 \item The compatibility between $\star$ and $\llbracket\blank,\blank\rrbracket$ in $G \oplus V^{\rev}$ implies the following \emph{mixed Leibniz rules} (see \cite[Def.~2.1]{Kowalzig2015}):
  \begin{align}
	  \iota_{\{x,y\}} \alpha &= \Lie_x \iota_y \alpha - (-1)^{(|x|-1)|y|} \iota_y \Lie_x \alpha, \\
	  \Lie_{x \wedge y} \alpha &= \iota_x \Lie_y \alpha + (-1)^{|x||y|} \iota_y \Lie_x \alpha. \label{eq:mixedleib}
  \end{align}
  \item The use of the reverse grading on $V$ in the definition ensures that for any homogeneous $x \in G^k$, the operators $\iota_x$ and $\Lie_x$ have degrees $-k$ and $1-k$, respectively, when viewed as endomorphisms of $V$.
}
%-----------------------------------------------------------+

>>>>

%-----------------------------------------------------------+
\subsection{Lie--Rinehart Algebras}
%-----------------------------------------------------------+

@@

  \begin{defblock}[Lie-Rinehart Algebra]
    A \underline{triple} $(A,\mathfrak{L},\rho)$ where
    \begin{itemize}[label=$\triangleright$]
      \item $A$ is a commutative, associative algebra,
      \item $\mathfrak{L}$ is an $A$-module and a Lie algebra,
      \item $\rho: \mathfrak{L} \to \mathrm{Der}(A)$ is an $A$-linear maps satisfying the Leibniz rule:

@@

\end{frame}
\note[itemize]{
    \item Let ${A}$ be a commutative  algebra over a field $\mathbb{k}$.
  Denote by $\X(A)=\Der_{\mathbb{k}}(A)$ its Lie algebra of derivations, which naturally forms an $A$-submodule of $\End(A)$ with the action $A\curvearrowright \End(A)$ given by postmultiplying with the element of $A$.
  \item In the context of differential geometry, a primary example is when $A = C^\infty(M)$, the algebra of smooth functions on a smooth manifold $M$. In this case, $\mathfrak{X}(A)$ is isomorphic to the standard $C^\infty(M)$-module of smooth vector fields on $M$, often denoted by $\mathfrak{X}(M)$.
  \item To generalize the above geometric structures, we introduce the algebraic counterparts of  "multivector fields " and  "differential forms with Cartan calculus. " 
  \item The anchor map $\rho: E \to \mathop{\mathrm{Der}}(A)$ abstractly encodes the notion of derivations of $A$ with an $A$-linear Lie bracket. 
  \item   In fact, Lie-Rinehart algebras are algebraic analogues of Lie algebroids (and every Lie algebroid gives a Lie-Rinehart algebra).
  \item singular foliations in the sense of Androulidakis and Skandalis can be viewed as Lie--Rinehart algebras
  \item a Lie--Rinehart algebra over $C^{\infty}(M)$ that is projective as a module is equivalent to a Lie algebroid,  
}
%-----------------------------------------------------------+

%-----------------------------------------------------------+
\subsection{Gerstenhaber Algebras and Modules}
%-----------------------------------------------------------+

@@

  \begin{quote}
    \centering
    \emph{... generalize the structure of the exterior algebra of multivector fields ...}
  \end{quote}
  %
  \begin{defblock}[Gerstenhaber Algebra]
    A \underline{triple} $(G, \wedge, \lbrace\cdot,\cdot\rbrace)$ where
    \begin{itemize}[label=$\triangleright$]
		\item $G$ is a $\mathbb{Z}$-graded vector space;
		\item $\wedge : G \otimes G \to G$ is a graded commutative, associative product;
		\item $\{\cdot,\cdot\} :G[1]\otimes G[1]\to G[1]$ is a graded Lie bracket,
  \end{itemize}
Compatibility: The bracket is a derivation of $\wedge$:
	\begin{align*}\label{eq:Gerstenhaber-derivationProperty}
		\{a, b \wedge c\} = \{a, b\} \wedge c + (-1)^{(|a|-1)|b|} b \wedge \{a, c\}
		&& \forall~ a, b, c \in G.
	\end{align*}

@@

\end{frame}
\note[itemize]{
  \item  The bracket $\{\cdot,\cdot\}$ could also be reinterpreted as a degree $-1$ bracket on the desuspended $\Z$-graded vector space $G$, coincides with the definition of $1$-Poisson algebra of \cite{Cattaneo2006b}.
  \item The Schouten--Nijenhuis bracket is the unique graded Lie bracket satisfying the following properties:
\begin{itemize}
	\item It restricts to the given Lie bracket on $\Lambda_A^1 \mathfrak{L} = \mathfrak{L}$;
	\item It vanishes on $A = \Lambda_A^0 \mathfrak{L}$;
	\item It satisfies the graded Leibniz rule with respect to the wedge product.
\end{itemize}
%
Explicitly, for homogeneous elements $x_1, \dots, x_m, y_1, \dots, y_n \in \mathfrak{L}$ and $f \in A$, it is given by
\begin{align*}
	[x_1 \wedge \cdots \wedge x_m,\; y_1 \wedge \cdots \wedge y_n] 
	&= \sum_{i,j} (-1)^{i+j} [x_i, y_j] \wedge x_1 \wedge \cdots \widehat{x_i} \cdots \wedge x_m \wedge y_1 \wedge \cdots \widehat{y_j} \cdots \wedge y_n~.
\end{align*}
}
%-----------------------------------------------------------+

@@

  \begin{exblock}[Chevalley--Eilenberg Algebra]
    The Chevalley--Eilenberg algebra for the Lie-Rinehart algebra $(A,\mathfrak{L},\rho)$:
    $$
    \CE(\mathfrak{L}) := \left((\Lambda_A^\bullet \mathfrak{L})^*\right)^{\rev}
    $$ 
    \smallskip

@@

%-----------------------------------------------------------+
\subsection{Cartan Calculus}
%-----------------------------------------------------------+

%-----------------------------------------------------------+
\begin{frame}{BV-Modules}
  %
  \begin{quote}
    \centering
    \emph{... generalize the structure of (the de Rham) algebra ...}
  \end{quote}
  %
  \begin{defblock}[Batalin-Vilkovisky Module]
    Is a \underline{graded vector space} $V$ together with
    \begin{itemize}[label=$\triangleright$]
      \item a differential $\d: V^i \to V^{i+1}$ (i.e. $d^2=0$),
      \item a Gerstenhaber module structure over a Gerstenhaber algebra $(G, \wedge, \lbrace\cdot,\cdot\rbrace)$,
    \end{itemize}
    Compatibility wrt the Lie algebra action $\Lie:G\curvearrowright V$: 
    $$
      \Lie_x = [\iota_x, \d]~, \qquad \forall x \in G~.
    $$
  \end{defblock}
  \vfill\pause

@@

%-----------------------------------------------------------+
\begin{frame}{Abstract Cartan Calculus}
  %
  \begin{quote}
    \centering
    \emph{a BV-module $(V,\d)$ over $(G,\wedge,\lbrace\cdot,\cdot\rbrace)$ encodes a full Cartan calculus}
  \end{quote}
  %
  \vfill\pause
  \begin{denotblock}
    \begin{itemize}
      \item $\d$ the degree $1$ differential on $V$;
	    \item $\iota$ the associative algebra action\footnote{$\iota_{x\wedge y}=\iota_x\iota_y~, \qquad \forall x,y\in G$.} of $(G,\wedge)$ on $V$;
  	  \item $\Lie$ the Lie algebra action
      of $(G,\{\cdot,\cdot\})$ on $V$ of degree $-1$.
    \end{itemize}   
  \end{denotblock}
  \vfill\pause

  \begin{lemblock}[Cartan identities]
 The operators $\d$, $\iota_x$, and $\Lie_x$ satisfy six\footnote{There's also: $\Lie_{x\wedge y}=\iota_x\Lie_y + (-1)^{|y|}\Lie_x \iota_y~, \qquad \forall  x,y\in G$.}  graded commutation relations:
	%
  \begin{align*}
	  \d^2                            &= 0,            &&&
	\iota_X \iota_Y + \iota_Y \iota_X  &= 0 ~,         \\
\iota_X \d   +	\d \iota_X      &= \Lie_X ~,    &&&
	\d \Lie_X - \Lie_X \d          &= 0 ~,    \\
	\Lie_X \iota_Y - \iota_Y \Lie_X    &= \iota_{[X,Y]}~,  &&&
	\Lie_X \Lie_Y - \Lie_Y \Lie_X      &= \Lie_{[X,Y]}~. 
\end{align*}
	%
  \end{lemblock}
  \vfill\pause

  \begin{exblock}[Classical Cartan Calculus]
    \vspace{-0.5em}
    $$ A=C^\infty(M)~,  \quad \mathfrak{L}=\X(M)~,\quad
     G=\Lambda^\bullet \X(M)~, \quad V=\Omega^\bullet(M)~. $$
  \end{exblock}
  %
\end{frame}
\note[itemize]{
  \item 	A pair $(G, V)$ consisting of a Gerstenhaber algebra and a BV module is often called a \emph{Tsygan–Tamarkin–Nest noncommutative differential calculus}~\cite[Def.~4.4]{Tsygan2004}.
  \item Denote Gerstenhaber algebra structure on $G \oplus V^{\rev}$ by $(\star,\llbracket\cdot,\cdot\rrbracket)$. For a homogeneous element $x \in G$, denote by $\iota_x$ and $\Lie_x$ the corresponding operators on $V$.
  \item These actions are induced by restricting the Gerstenhaber structure $(\star,\llbracket\cdot,\cdot\rrbracket)$ on $G \oplus V^{\rev}$ to $G \otimes V^{\rev} \subset (G \oplus V^{\rev})^{\otimes 2}$.
 \item The associative action $\iota$ is defined by
	\[
	\morphism{\iota}{G \otimes V^{\rev}}{V^{\rev}}{(x,\alpha)}{\iota_x \alpha := x \star \alpha},
	\]
	and satisfies
	\[
	\iota_{x \wedge y} \alpha = \iota_x \iota_y \alpha \quad \text{and} \quad \iota_x \alpha = (-1)^{|x||\alpha|} \alpha \star x.
	\]

	\item The Lie action $\Lie$ is defined by
	\[
	\morphism{\Lie}{G \otimes V^{\rev}}{V^{\rev}[-1]}{(x,\alpha)}{\Lie_x \alpha := \llbracket x, \alpha \rrbracket},
	\]
	and satisfies
	\[
	\Lie_{\{x,y\}} \alpha = \Lie_x \Lie_y \alpha + (-1)^{(|x|-1)(|y|-1)} \Lie_y \Lie_x \alpha,
	\]
	as well as the graded antisymmetry identity
	\[
	\Lie_x \alpha = -(-1)^{|x||\alpha|} \llbracket \alpha, x \rrbracket.
	\]
 \item The compatibility between $\star$ and $\llbracket\cdot,\cdot\rrbracket$ in $G \oplus V^{\rev}$ implies the following \emph{mixed Leibniz rules} (see \cite[Def.~2.1]{Kowalzig2015}):
  \begin{align}
	  \iota_{\{x,y\}} \alpha &= \Lie_x \iota_y \alpha - (-1)^{(|x|-1)|y|} \iota_y \Lie_x \alpha, \\
	  \Lie_{x \wedge y} \alpha &= \iota_x \Lie_y \alpha + (-1)^{|x||y|} \iota_y \Lie_x \alpha. \label{eq:mixedleib}
  \end{align}
  \item The use of the reverse grading on $V$ in the definition ensures that for any homogeneous $x \in G^k$, the operators $\iota_x$ and $\Lie_x$ have degrees $-k$ and $1-k$, respectively, when viewed as endomorphisms of $V$.
}
%-----------------------------------------------------------+

### 2025-10-24 bv-triples-intro.tex
Presentation done.

%----------------------------------------------------+
\begin{frame}[fragile]{Keywords}
\tikzstyle{every picture}+=[remember picture]
	\begin{columns}
    	\begin{column}{.45\textwidth}
    		\onslide<5->{
			\tikz[baseline]{
		            \node[draw=orange!40,anchor=base,text width=5cm] (s1)
		            {The procedure to reduce the dimensions of Phase Space (e.g. of the space of measurable quantities) in presence of constraints or symmetries.};
			}
		}
	\end{column}
    	\begin{column}{.45\textwidth}
    		\onslide<4->{
			 \tikz[baseline]{
		            \node[draw=blue!40,anchor=base, text width=5cm] (s2)
		            {Higher analogue of DGLie algebras where Jacobi holds up to homotopies.};
			}
		}
	\end{column}
	\end{columns}

>>>>

%----------------------------------------------------+
\begin{frame}[fragile]{Keywords}
\tikzstyle{every picture}+=[remember picture]
	\begin{columns}
    	\begin{column}{.45\textwidth}
    		\onslide<5->{
			\tikz[baseline]{
		            \node[draw=orange!40,anchor=base,text width=5cm] (s1)
		            {The procedure to reduce the dimensions of a Phase Space (or the space of obsevables) in presence of constraints or symmetries.};
			}
		}
	\end{column}
    	\begin{column}{.45\textwidth}
    		\onslide<4->{
			 \tikz[baseline]{
		            \node[draw=blue!40,anchor=base, text width=5cm] (s2)
		            {Higher analogue of DGLie algebras where Jacobi holds up to homotopies.};
			}
		}
	\end{column}
	\end{columns}

### 2025-10-24 bv-triples-main.tex
Corrected problem with flags
Presentation done.

%- HandOut Flag -----------------------------------------------------------------------------------------
	\newif\ifHandout
	\Handouttrue  %uncomment for the printable version
	%Handling of flags it is not preserved when passing to standalone-subfiles!

@@

	{\vskip 1ex}
	\href{https://www.mat.uniroma2.it/~ricerca/algebr/page-AREA_files/page-AREA-2_files/talks.html}{- ARTS - Algebra and Representation Theory Seminar in Roma "Tor Vergata"}
	\\
	Universit\'a di Roma - Tor Vergata, October 2025
}

@@

%----------------------------------------------------------------------------------+
\begin{frame}  % Alternative: \maketitle outside of frame
	\titlepage
	\ifHandout
		\tikz[overlay,remember picture]
		{
	    	%	\node at ($(current page.west)+(1.5,0)$) [rotate=90] {\Huge\textcolor{gray}{\today}};
	    	\node[        
	    		draw,
	    		shape border rotate=90,
			isosceles triangle,
			isosceles triangle apex angle=90,
			fill=yellow]
	        		at ($(current page.north east)-(1,1)$) [rotate=-45] {\textcolor{red}{Handout version}};
		}
	\fi
\end{frame}
\addtocounter{framenumber}{-1}
\note{
	%\textbf{\underline{OUTLINE}}:
	%\tableofcontents
	\textbf{Abstract:}
	\\
	\footnotesize
Multisymplectic manifolds generalize symplectic manifolds by carrying a closed, nondegenerate differential form of degree higher than 2. Such structures naturally arise in the geometric formulation of classical field theories.
Rogers (2010) showed that, just as a symplectic manifold yields a Poisson algebra of functions, an n-plectic manifold gives rise to an n-term Lie infinity algebra of observables.
Remarkably, his construction is purely algebraic and based only on Cartan calculus, suggesting that this higher “Poisson algebra” can be generalized beyond manifolds.
In this talk, we present such a generalization within the setting of Gerstenhaber algebras and Batalin–Vilkovisky (BV) modules, which provide an algebraic formulation of Cartan calculus relevant to noncommutative geometry.
This framework allows us to define Lie infinity algebras of observables in a fully algebraic way, without referring to an underlying manifold.
As an application, we address the reduction of multisymplectic observables in the presence of constraints or symmetries. Building on the work of Dippel, Esposito, and Waldmann on “constraint triples” for coisotropic reduction, we adapt this formalism to BV-modules and their Lie infinity algebras.
This yields a conceptual setting for the algebraic reduction of multisymplectic observables, as developed in our joint work with Casey Blacker (SIGMA 2024).
The results are part of a collaboration with Leonid Ryvkin, published in *Differential Geometry and its Applications* (2025).

@@

			\begin{upshotblocktitle}[Recovered previous reduction procedures]
				 Emploied this machinery to provide a conceptual framework for algebraic multisymplectic reduction of observables via constraint triples 
				 \smallskip

				 \fullcite{Blacker-M-Ryvkin-2024}\nocite{Blacker-M-Ryvkin-2024}
			\end{upshotblocktitle}
			\vfill\pause

>>>>

%- HandOut Flag -----------------------------------------------------------------------------------------
	\newif\ifHandout\Handoutfalse
	\Handouttrue  %uncomment for the printable version
	%Handling of flags it is not preserved when passing to standalone-subfiles!

@@

	{\vskip 1ex}
	\href{https://www.mat.uniroma2.it/~ricerca/algebr/page-AREA_files/page-AREA-2_files/talks.html}{- ARTS - Algebra and Representation Theory Seminar}
	\\
	Universit\'a di Roma - Tor Vergata, October 2025
}

@@

%----------------------------------------------------------------------------------+
\begin{frame}  % Alternative: \maketitle outside of frame
	\titlepage
	% Handout watermark
	\ifHandout
		\tikz[overlay,remember picture]
		{
	    	%	\node at ($(current page.west)+(1.5,0)$) [rotate=90] {\Huge\textcolor{gray}{\today}};
	    	\node[        
	    		draw,
	    		shape border rotate=90,
			isosceles triangle,
			isosceles triangle apex angle=90,
			fill=yellow]
	        		at ($(current page.north east)-(1,1)$) [rotate=-45] {\textcolor{red}{Handout version}};
		}
	\fi
	% European Commission	
		\tikz[overlay,remember picture]
		{
	    	%	\node at ($(current page.west)+(1.5,0)$) [rotate=90] {\Huge\textcolor{gray}{\today}};
	    	\node[        
	    		text width = 3.5cm
			]
	        		at ($(current page.south west)+(2.0,2.0)$) [rotate=0] {

					\href{https://dipartimenti.unicatt.it/dmf-home?rdeLocaleAttr=it}{\includegraphics[width=\textwidth]{./Logos/Eu-h2020}}

	        		};
		}
	\end{frame}
\addtocounter{framenumber}{-1}
\note{
	%\textbf{\underline{OUTLINE}}:
	%\tableofcontents
	\textbf{Abstract:}
	\\
	\footnotesize
Multisymplectic manifolds generalize symplectic manifolds by carrying a closed, nondegenerate differential form of degree higher than 2. Such structures naturally arise in the geometric formulation of classical field theories.
Rogers (2010) showed that, just as a symplectic manifold yields a Poisson algebra of functions, an n-plectic manifold gives rise to an n-term Lie infinity algebra of observables.
Remarkably, his construction is purely algebraic and based only on Cartan calculus, suggesting that this higher “Poisson algebra” can be generalized beyond manifolds.
In this talk, we present such a generalization within the setting of Gerstenhaber algebras and Batalin–Vilkovisky (BV) modules, which provide an algebraic formulation of Cartan calculus relevant to noncommutative geometry.
This framework allows us to define Lie infinity algebras of observables in a fully algebraic way, without referring to an underlying manifold.
As an application, we address the reduction of multisymplectic observables in the presence of constraints or symmetries. Building on the work of Dippel, Esposito, and Waldmann on “constraint triples” for coisotropic reduction, we adapt this formalism to BV-modules and their Lie infinity algebras.
This yields a conceptual setting for the algebraic reduction of multisymplectic observables, as developed in our joint work with Casey Blacker (SIGMA 2024).
The results are part of a collaboration with Leonid Ryvkin, published in *Differential Geometry and its Applications* (2025).

@@

			\begin{claimblocktitle}[Recovered previous reduction procedures]
				 Emploied this machinery to provide a conceptual framework for algebraic multisymplectic reduction of observables via constraint triples 
				 \smallskip

				 \fullcite{Blacker-M-Ryvkin-2024}\nocite{Blacker-M-Ryvkin-2024}
			\end{claimblocktitle}
			\vfill\pause

### 2025-10-24 bv-triples-reduction.tex
Presentation done.

@@

%
\begin{defblock}[Constraint Gerstenhaber algebra {(\cite[Def. 2.25]{dippelkern})}]
	A constraint algebra $G=\triple{G}$ equipped with a constraint bilinear map
	\begin{displaymath}
		\{ \blank, \blank \} \colon G[1] \otimes G[1] \to G[1]
	\end{displaymath}
	such that $G_\Total$ is a Gerstenhaber algebra. 
\end{defblock}
\pause\vfill
%

 \begin{remblock}[$G$ can be seen as a triple of Gerstenhaber subalgebras]\label{rk:constraintgerst-as-triple}
	 $G_\Null \subseteq G_\Wobs \subseteq (G_\Total, \wedge,\lbrace\blank,\blank\rbrace)$ such that $G_\Null$ is a Gerstenhaber ideal in $G_\Wobs$. 
\end{remblock}
\pause\vfill
%

>>>>

%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
\begin{frame}{A plethora of approaches to singular reduction}
 	Many singular reduction schemes adhere to this pattern!
 	\vfill
 	\pause
\begin{table}[]
	\begin{tabular}{l|l|l||l}
		algebra $\mathcal{A}_T$ & subalgebra $\mathcal{A}_N$ & ideal $\mathcal{A}_0$ & comment \\
		\hline

		$C^\infty(M)$&      $N_S$     &   $I_S$   &  $\substack{S=\mu^{-1}(0),~ I_S=\{f~|~f|_S=0\}}$ \\
			&&&  $\substack{N_S= \{ f | gf-f\in I_S \forall g\in G\}}$ \\
	& & & \color{red} not Poisson \\ 
	\hline	\pause
	$C^\infty(M)$&   $F_S$         &   $I_S$   &  $\substack{F_S=\{f~|~\{f,I_S\}\subset I_S\}}$ \\
	& & & \color{red} if $I_S\subset F_S$\\
	\hline \pause

	$C^\infty(M)$&   $C^\infty(M)^G$         &   $(I_S)^G$   &  $\substack{C^\infty(M)^G=\{f~|~gf=f\forall g\in G\}}$ \\
	\hline \pause
		$C^\infty(M)$&   $C^\infty(M)^G$         &   $(I_\mu)^G$   & $\substack{I_\mu=\{\sum_{i=1}^k f_i\langle \mu,\xi_i\rangle|~f_i\in C^\infty(M), \xi_i\in \mathfrak g\}}$\\
		\hline \pause
	$C^\infty(M)$&      $N_\mu$     &   $I_\mu$   & $\substack{N_\mu= \{ f | gf-f\in I_\mu \forall g\in G\}}$ \footnote{When $G$ connected $N_\mu=N(I_\mu):=\{f~|~\{f,I_\mu\}\subset I_\mu\}$.}\\
	\hline

	\end{tabular}\pause
\end{table}
	\vfill
	{\bf Remarks }names in order: 'naive' , Dirac, Sniatycki, Arms-Cushman-Gotay, Sniatycki-Weinstein.

\end{frame}
\note[itemize]{
	\item \emph{(Credits to \href{https://www.ryvkin.eu/}{Leonid Ryvkin} for the tex code of this slide.)}
}
%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%

@@

%
\begin{defblock}[Constraint Gerstenhaber algebra {(\cite[Def. 2.25]{dippelkern})}]
	A constraint algebra $G=\triple{G}$ equipped with a constraint bilinear map
	\begin{displaymath}
		\{ \cdot, \cdot \} \colon G[1] \otimes G[1] \to G[1]
	\end{displaymath}
	such that $G_\Total$ is a Gerstenhaber algebra. 
\end{defblock}
\pause\vfill
%

 \begin{remblock}[$G$ can be seen as a triple of Gerstenhaber subalgebras]\label{rk:constraintgerst-as-triple}
	 $G_\Null \subseteq G_\Wobs \subseteq (G_\Total, \wedge,\lbrace\cdot,\cdot\rbrace)$ such that $G_\Null$ is a Gerstenhaber ideal in $G_\Wobs$. 
\end{remblock}
\pause\vfill
%
